### 2023-12-24 main.tex
''

\paragraph{Organization of the paper and main results.}
We start in Section~\ref{sec1} by defineing the open multispecies stirring
process on a general graph and providing its Lie algebraic description in terms of the generators of the $gl(N)$ Lie algebra. In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
and show that the problem of characterizing the non-equilibrium
steady state can be reduced to the computation of the absorption probabilities similar to the single-species case on the line  \cite{KMP} and for a general graph \cite{ frassek2020duality}.  
In Section~\ref{sectionIntegrabiliy}  we consider  the case of the one-dimensional chain with at most one 
particle per site ($\nu=1$), which is driven out-of-equilbrium by two reservoirs on the left and right boundaries. In this case we obtain a closed-form expression for the stationary correlations (Theorem~\ref{thm-correlations}). Here the computation
% of the absorption probabilities 
relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact} and the $gl(N)$ invariance of the process in the bulk. Finally in Section~\ref{sec5} we discuss a few extensions 
and generalizations of the model. 
The first generalization is the formula for the correlations for the boundary driven chain in the case when more than one particle is allowed at each site ($\nu > 1$). 
In this situation integrability is lost and we cannot derive explicit formulas for the absorption probabilities. However, in Appendix \ref{appendix-1pts-general}, we show how to compute the one-point correlation by using the properties of a random walk. The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process and the formulation of the the absorbing duality with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}). Finally, the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities (inspired by \cite{casini2022uphill,schutzReaction}). 
We report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD}. 
Again, an absorbing duality is proved with the same duality function of the multispecies stirring process.

@@

% For recent examples in the framework of singlespecies systems, see \cite{frassek2020eigenstates, frassek2020duality,frassek2022exact}.
% {\color{red}
% Here we generalize the duality approach to the set-up of multispecies particle systems.}

@@

\subsection{Strategy}
 In the next Section~\ref{subsection-exact} we will show that the DEHP albegra in \eqref{bulk}-\eqref{rightBoundary} can be simplified substantially using the ${gl}(N)$ invariance of the bulk. In fact, such simplification can always be achieved if 
  there exists an absorbing dual process as established in Section~\ref{sectionDuality}

@@

\subsection{The single-species case (SSEP)}
The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {i.e. when only one type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations of SEEP: 

>>>>

\paragraph{Organization of the paper and main results.}
We start in Section~\ref{sec1} by defineing the open multispecies stirring
process on a general graph and providing its Lie algebraic description in terms of the generators of the $gl(N)$ Lie algebra. In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
and show that the problem of characterizing the non-equilibrium
steady state can be reduced to the computation of the absorption probabilities similar to the single species case on the line  \cite{KMP} and for a general graph \cite{ frassek2020duality}.  
In Section~\ref{sectionIntegrabiliy}  we consider  the case of the one-dimensional chain with at most one 
particle per site ($\nu=1$), which is driven out-of-equilbrium by two reservoirs on the left and right boundaries. In this case we obtain a closed-form expression for the stationary correlations (Theorem~\ref{thm-correlations}). Here the computation
% of the absorption probabilities 
relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact} and the $gl(N)$ invariance of the process in the bulk. Finally in Section~\ref{sec5} we discuss a few extensions 
and generalizations of the model. 
The first generalization is the formula for the correlations for the boundary driven chain in the case when more than one particle is allowed at each site ($\nu > 1$). 
In this situation integrability is lost and we cannot derive explicit formulas for the absorption probabilities. However, in Appendix \ref{appendix-1pts-general}, we show how to compute the one-point correlation by using the properties of a random walk. The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process and the formulation of the the absorbing duality with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}). Finally, the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities (inspired by \cite{casini2022uphill,schutzReaction}). 
We report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD}. 
Again, an absorbing duality is proved with the same duality function of the multispecies stirring process.

@@

% For recent examples in the framework of single species systems, see \cite{frassek2020eigenstates, frassek2020duality,frassek2022exact}.
% {\color{red}
% Here we generalize the duality approach to the set-up of multispecies particle systems.}

@@

\subsection{Strategy}
 In the next Section~\ref{subsection-exact} we will show that the DEHP algebra in \eqref{bulk}-\eqref{rightBoundary} can be simplified substantially using the ${gl}(N)$ invariance of the bulk. In fact, such simplification can always be achieved if 
  there exists an absorbing dual process as established in Section~\ref{sectionDuality}

@@

\subsection{The single species case (SSEP)}
The computations made for the multispecies stirring process can be specialized to the single species case $N=2$, {i.e. when only one type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations of SEEP: 
